### 2016-10-04 Paper_v8.tex
RG JB patches

The control terms $0\leq v_{j}\leq 1$ depended upon the combination of factors which influenced rate process $j$.
For each rate, we used a rule-based approach to select from competing control factors.
If rate $j$ was influenced by $1,\dots,m$ factors, we modeled this relationship as
$v_{j}=\mathcal{I}_{j}\left(f_{1j}\left(\cdot\right),\hdots,f_{mj}\left(\cdot\right)\right)$
where $0\leq f_{ij}\left(\cdot\right)\leq 1$ denotes a regulatory transfer function quantifying the influence of factor $i$ on rate $j$.
The function $\mathcal{I}_{j}\left(\cdot\right)$ is an integration rule which maps the output of regulatory transfer functions into a control
variable. In this study, we used $\mathcal{I}_{j}\in\left\{min,max\right\}$ and hill transfer functions \cite{pr3010178,pr3010138}.
If a process has no modifying factors, $v_{j}=1$.

@@

\subsection*{Cell culture and experimental interrogation}
DLD1 colon carcinoma, MCF10A, and HUVEC were acquired from the American Tissue Culture Collection (Manassas, VA). Cells were grown in culture with RPMI 1640 medium with 10\% fetal bovine serum and 1\% penicillin/streptomycin for DLD1, EBM-2 supplemented with EGM-2, 5\% fetal bovine serum, and 1\% penicillin/streptomycin for HUVEC, or MGEM 2 supplemented with insulin, bovine pituitary extract, cholera toxin, hEGF, hydrocortisone, 5\% horse serum, and 1\% penicillin/streptomycin for MCF10A. Cells were serum starved for 24 hours and removed from all experimental conditions.  Recombinant VEGFA165 was also removed from culture medium prior to experimentation.  Recombinant human TGF$-\beta$2 (R$\And$D Systems, Minneapolis, MN) was added to the culture medium at a concentration of 10 ng/ml and recombinant VEGFA165 at a concentration of (5ng/ml, 50ng/ml) for all relative experiments.  NFAT inhibitor (VIVIT peptide) (EMDBiosciences, Darmstadt, Germany), was added to the culture medium at a concentration of 10$\mu$M for all relative experiments.   Cells were passaged 1:3 or 1:4 every 3-6 d and used between passages 4 and 8.

\subsubsection*{VEGF treatment}
DLD1 and MCF10A cells were suspended in culture media (with RPMI 1640 medium with 10\% fetal bovine serum and 1\% penicillin/streptomycin for DLD1 or MGEM 2 supplemented with insulin, bovine pituitary extract, cholera toxin, hEGF, hydrocortisone, 5\% horse serum, and 1\% penicillin/streptomycin for MCF10A), and allowed to aggregate overnight in hanging drop culture (20$\mu$L; 20,000 cells).  The spherical aggregates were placed on the surface of neutralized type I collagen hydrogels (1.5mg/mL) and allowed to adhere.  Cultures were then serum starved (1\% serum) for 24 hours.  Recombinant VEGFA165 was then added to the media (5ng/ml, 50ng/ml) and mRNA was harvested after 3hr and 24hr timepoint.

>>>>

The control terms $0\leq v_{j}\leq 1$ depended upon the combination of factors which influenced rate process $j$.
For each rate, we used a rule-based approach to select from competing control factors.
If rate $j$ was influenced by $1,\dots,m$ factors, we modeled this relationship as
$v_{j}=\mathcal{I}_{j}\left(f_{1j}\left(\cdot\right),\hdots,f_{mj}\left(\cdot\right)\right)$
where $0\leq f_{ij}\left(\cdot\right)\leq 1$ denotes a regulatory transfer function quantifying the influence of factor $i$ on rate $j$.
The function $\mathcal{I}_{j}\left(\cdot\right)$ is an integration rule which maps the output of regulatory transfer functions into a control
variable. In this study, we used $\mathcal{I}_{j}\in\left\{min,max\right\}$ and hill transfer functions \cite{pr3010178,pr3010138}.
If a process has no modifying factors, $v_{j}=1$. Factors can be individual metabolite or protein levels or some function, e.g., the product of metabolite levels. In the current study, we let factors correspond to the abundance of individual proteins, inhibitors or transcription factors, as well as products of transcription factors where it is necessasry to represent a co-dependent regulatory activity.

@@

\subsection*{Cell culture and experimental interrogation}
DLD1 colon carcinoma and MCF10A cells were acquired from the American Tissue Culture Collection (Manassas, VA). Cells were grown in culture with RPMI-1640 medium with 10\% fetal bovine serum and 1\% penicillin/streptomycin or MGEM-2 supplemented with insulin, bovine pituitary extract, cholera toxin, hEGF, hydrocortisone, 5\% horse serum, and 1\% penicillin/streptomycin, respectively.  Cells were passaged 1:3 or 1:4 every 3-6 d and used between passages 4 and 8.  During treatment regime, DLD1 and MCF10A cells aggregated overnight in hanging drop culture (20$\mu$L; 20,000 cells).  The spherical aggregates were placed on the surface of neutralized type I collagen hydrogels (1.5mg/mL) and allowed to adhere.  Cultures were then serum starved (1\% serum) for 24 hours.  Recombinant human TGF$-\beta$2 (R$\And$D Systems, Minneapolis, MN) was added to the culture medium at a concentration of 10 ng/ml and recombinant VEGFA165 at a concentration of (5ng/ml, 50ng/ml) for all relative experiments.  NFAT inhibitor (VIVIT peptide) (EMDBiosciences, Darmstadt, Germany), was added to the culture medium at a concentration of 10$\mu$M for all relative experiments.  mRNA was then harvested at both the 3hr and 48hr time-point.
